Object detection for Verification Based Annotation

### 2019-09-09 paper.tex
Updates from Overleaf

We use \gls{AP} at different levels of \gls{IOU} threshold for evaluation, this is the \gls{AP} across all examples and not a \gls{mAP}, (largely academic because most datasets here are single class). $AP_{COCO}$ is defined as the mean of $AP_t$ for $t \in [0.5, 0.55..0.95]$.

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/incremental.pdf}
  \caption{Incrementally adding examples vs. training with all examples from the beginning. Dotted lines are incremental training, solid lines are training with all examples up front. Grey lines at the bottom of each chart show the training loss.}  
  \label{fig:incremental}
\end{figure}

>>>>

We use \gls{AP} at different levels of \gls{IOU} threshold for evaluation. This is the \gls{AP} across all examples and not a \gls{mAP} (largely academic because most datasets here are single class). This is notated $AP_{t}$ for \gls{IOU} threshold $t$. In particular two thresholds we use are $AP_{50}$ for a relaxed matching threshold and $AP_{75}$ for a strict threshold and then $AP_{COCO}$ for an average over a range of thresholds. $AP_{COCO}$ is defined as the mean of $AP_t$ for $t \in [0.5, 0.55..0.95]$.

\subsection{Training parameters}

In all experiments in this work I use a \gls{SGD} optimiser with the base learning rate set to $0.001$, momentum $0.9$ and weight decay $0.0001$ in all cases. Total loss is averaged across each mini-batch, and batch sizes of $8$ are used. The balance factor between localisation and classification loss is $\lambda=2.5$ in all cases. A cyclical learning rate is used during over each batch, with a log interpolated (geometric) multiplier reducing the learning rate by a factor of $0.1$ at the end of the batch.

Image augmentation is used, crops taken at varied scale (${3/4}$--${4/3}$) and aspect ratio ($\pm 10\%$), flips ($0.5$ probability). A range of photo-metric augmentations: brightness ($\pm 10\%$), contrast ($\pm 10\%$), gamma adjustment ($\pm 0.1\%$), hue ($\pm 5$) and saturation ($\pm 5$) adjustment.

Code for this paper can be found \href{https://github.com/saulzar/detection/tree/thesis}{here}, under the tag ``thesis'', with details surrounding the cropping procedure, default training and augmentation parameters etc.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=1.0\linewidth]{figures/incremental.pdf}
  \caption{Incrementally adding examples vs. training with all examples from the beginning. Dotted lines are incremental training, solid lines are training with all examples up front. Grey lines at the bottom of each chart show the training loss.}  
  \label{fig:incremental}
\end{figure}
